### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@bc9240fb23f3a10cd351dcf87d589d8085c768cf 🚀

@@

Now that we have a metaweb\ldots..

>>>>

What does this tell us? The ensemble model is regularlly the best for
ROC, but not for PR. This illustrates a tradeoff between models being as
``right'' as possible versus a model being useful for discovering
false-negatives.

@@

Now that we have a metaweb, we can extend this to predict interactions
at partilar places and times by decomposing the probability of
interaction at particular place and time into probability of interaction
times probability of cooccurrence via properties of conditional prob.
(Gravel \emph{et al.} 2019)

\(P(A_{ij})P(O_{ij})\) vs \(P(A_{ij})P(O_i)P(O_j)\)
